---
title: "lab6pkg"
author: "Aqsa, Oliver and Samira"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab6pkg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lab6pkg)
```


```{r}
suppressWarnings(RNGversion("3.5.9"))
set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
n <- 2000
knapsack_objects <- data.frame(
  w=sample(1:4000, size = n, replace = TRUE),
  v=runif(n = n, 0, 10000))
```

# **The Knapsack Problem**

This package contains three different functions for solving _the Knapsack Problem_:

**1. brute_force_knapsack**

**2. knapsack_dynamic**

**3. greedy_knapsack**

## First function: **brute_force_knapsack()**

The only solution that is guaranteed to give a correct answer in all situations for the knapsack problem is using brute-force search, i.e. going through all possible alternatives and return the maximum value found. This approach is of complexity $O(2^n)$ since all possible combinations $2^n$ needs to be evaluated.


The Algorithm can be executed as shown below. The time taken for $n=16$ objects is shown below.

```{r runCode, echo=TRUE}
set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
n <- 16
knapsack_objects <- data.frame(w=sample(1:4000, size = n, replace = TRUE),v=runif(n = n, 0, 10000))
brute_force_knapsack(knapsack_objects[1:16,],3500)
system.time(brute_force_knapsack(knapsack_objects[1:16,],3500))
```
RUN TIME with parallel equal to FALSE: 0.69 second
RUN TIME with parallel equal to FALSE: 0.19 second

<p> After Parallelizing, the run time shortened significantly.
 
<p> After profiling, it can be seen that it is taking too much time in serial operation.The time taken for $n=16$ objects.

```
 time           alloc          release       dups     
Min.   :0.001   Min.   :0.000   Min.   :0   Min.   : 890  
1st Qu.:0.001   1st Qu.:1.817   1st Qu.:0   1st Qu.:1347  
Median :0.001   Median :3.634   Median :0   Median :1804  
Mean   :0.001   Mean   :3.634   Mean   :0   Mean   :1804  
3rd Qu.:0.001   3rd Qu.:5.450   3rd Qu.:0   3rd Qu.:2262  
Max.   :0.001   Max.   :7.267   Max.   :0   Max.   :2719  
ref.Length  ref.Class    ref.Mode 
3           data.frame  list      
3           data.frame  list    
```

## Second function: **Knapsack_dynamic()**
<p> The Algorithm can be executed and the time taken for $n=500$ objects as shown below. As it can be seen that the dynamic algorithm is faster than the brute force because the dynamic algorithm will run in $O(Wn)$.

```{r}
set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
n <- 500
knapsack_objects <- data.frame(w=sample(1:4000, size = n, replace = TRUE),v=runif(n = n, 0, 10000))
knapsack_dynamic(knapsack_objects[1:12,],3500)
system.time(knapsack_dynamic(knapsack_objects,3500))

```
And the result of profiling comes below:

```
time           alloc          release       dups     
 Min.   :0.001   Min.   :0.000   Min.   :0   Min.   :1458  
 1st Qu.:0.001   1st Qu.:2.097   1st Qu.:0   1st Qu.:1988  
 Median :0.001   Median :4.193   Median :0   Median :2518  
 Mean   :0.001   Mean   :4.193   Mean   :0   Mean   :2518  
 3rd Qu.:0.001   3rd Qu.:6.290   3rd Qu.:0   3rd Qu.:3047  
 Max.   :0.001   Max.   :8.386   Max.   :0   Max.   :3577  
 ref.Length  ref.Class    ref.Mode 
 3           data.frame  list      
 3           data.frame  list 
 
```

## Third function: **greedy_knapsack()**
<p> The Algorithm can be executed and the time taken for $n=10000$ objects as shown below. Greedy algorithm is _not most accurate algorithm_, but is the fastest of all because the computational complexity for this algorithm is $O(nlogn)$ due to its sorting mechanism.  

```{r}
set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
n <- 10000
knapsack_objects <- data.frame(w=sample(1:4000, size = n, replace = TRUE),v=runif(n = n, 0, 10000))
greedy_knapsack(knapsack_objects[1:12,],3500)
system.time(greedy_knapsack(knapsack_objects[1:12,],3500))
```

And the result of profiling comes below:


```
      time           alloc         release       dups       
 Min.   :0.001   Min.   :0.00   Min.   :0   Min.   : 532.0  
 1st Qu.:0.001   1st Qu.:1.34   1st Qu.:0   1st Qu.: 920.8  
 Median :0.001   Median :2.68   Median :0   Median :1309.5  
 Mean   :0.001   Mean   :2.68   Mean   :0   Mean   :1309.5  
 3rd Qu.:0.001   3rd Qu.:4.02   3rd Qu.:0   3rd Qu.:1698.2  
 Max.   :0.001   Max.   :5.36   Max.   :0   Max.   :2087.0  
 ref.Length  ref.Class    ref.Mode 
 3           data.frame  list      
 3           data.frame  list      
```
